---
title: "Introduction to Binomial"
author: "Jason zhen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


# Binomial

The package `"binomial"` is a minimal self-implemented R package that contains functions for calculating probabilities for a Binomial Random Variable and related functions distribution and summary information, etc. 



## Finding the probability of a binomial 

There are three functions inside this package to calculate various probabilities of a binomial. They are `bin_probability()`, `bin_distribution()`, and `bin_cumulative()`. 

## bin_probabilities

`bin_probabilities()` takes three arguments: success, trials and probability of success. This function gives us the probability of obtaining that number of successes given the number of trials and probability of success of each trial. 


```{r}
bin_probability(success = 5,trials = 10, p = 0.3)
```


## bin_distribution

`bin_distribution()` takes two arguments: trials and prob. This function gives us the distribution of the ascending levels of success up to a constant number of trials and probability of success of each trial via a dataframe with classes bindis and data.frame. 

```{r}

bin1 <- bin_distribution(trials = 10,p = 0.3)
bin1
```


We can then run `plot()` on this bindis object to visualize the probabilities with a bar-graph to showcase the distribution for each success level given a constant number of trials. 

```{r}

plot(bin1)
```


## bin_cumulative

`bin_cumulative()` takes two arguments: trials and prob. This function gives us the cumulation of the ascending levels of success up to a constant number of trials and probability of success of each trial via a dataframe with classes bincum and data.frame.

```{r}
bin1 <- bin_cumulative(trials = 10,p = 0.3)
bin1
```

We can then run `plot()` on this bincum object to visualize the probabilities with a line-plot to showcase the cumulation of ascending success levels.

```{r}
plot(bin1)
```


## Creating a `binvar`, binomial variable object

To create a binomial variable object, use `bin_variable()`. This function takes two arguments, trials and probability of success. This is done so that the user can run `summary` on the binvar object to visualize summary measures: mean, variance, mode, skewness and kurtosis.

```{r}
bin1 <- bin_variable(trials = 10, p= 0.3)
summary(bin1)

```

